---
title: "Clustering Homework"
author: "Peter Menzies"
date: "15/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Clustering weekend

```{r, warning=F, message=F}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(broom)
library(animation)
```
```{r}
customers <- read_csv("mall_customers.csv") %>% 
  janitor::clean_names() %>% 
  rename(sex = gender)
```

```{r}
summary(customers)
```

* No NA's

##### Age

```{r}
customers <- customers %>% 
  select(-customer_id)

age_stats <- customers %>% 
  summarise(n = n(),
            mean = mean(age),
            sd = sd(age))

customers %>% 
  ggplot() +
  aes(x = age) +
  geom_histogram(aes(y = ..density..), colour = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = age_stats$mean,
      sd = age_stats$sd
    ),
    colour = "red"
  )

customers %>% 
  select(age) %>% 
  mutate(under_40 = age < 40) %>% 
  ggplot() +
  aes(x = under_40) +
  geom_bar()
```

* Age is fairly normally distributed, with more customers under 40

* A small increase at roughly age 65 = recently retired?


##### annual_income_k

```{r}
annual_inc_stats <- customers %>% 
  summarise(n = n(),
            mean = mean(annual_income_k),
            sd = sd(annual_income_k))

customers %>% 
  ggplot() +
  aes(x = annual_income_k) +
  geom_histogram(aes(y = ..density..), colour = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = annual_inc_stats$mean,
      sd = annual_inc_stats$sd
    ),
    colour = "red"
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10))

customers %>% 
  mutate(salary_range = case_when(
    annual_income_k < 50 ~ "A_ under 50k",
    annual_income_k >= 100 ~ "C_ over 100k",
    T ~ "B_ 50 to 100k")) %>% 
  ggplot() +
  aes(x = salary_range) +
  geom_bar()
```

* Normally-ish distributed, most common incomes roughly 55k - 75k 

```{r}
spending_score_1_100_stats <- customers %>% 
  summarise(n = n(),
            mean = mean(spending_score_1_100),
            sd = sd(spending_score_1_100))

customers %>% 
  ggplot() +
  aes(x = spending_score_1_100) +
  geom_histogram(aes(y = ..density..), colour = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = spending_score_1_100_stats$mean,
      sd = spending_score_1_100_stats$sd
    ),
    colour = "red"
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10))


```

* Normalish distribution - peaks around 50
                        -   then rises a bit at the extremes of the scale


##### sex

```{r}
customers %>% 
  ggplot() +
  aes(x = sex) +
  geom_bar()
```

* More female customers but fairly similar

##### summary

* An average customer may be either sex, aged under 40, earning between 50 and 100k and have a spending score of 50. 


### Scaling

```{r}
customers_scaled <- customers %>% 
  select(annual_income_k, spending_score_1_100) %>% 
  mutate(annual_income_k = scale(annual_income_k),
         spending_score_1_100 = scale(spending_score_1_100))
```

### Clustering

##### Elbow

```{r}
fviz_nbclust(customers_scaled, kmeans, method = "wss", nstart = 25)
```

* Hmm not totally convincing. Maybe 3 or 5?

#### sillhouette

```{r}
fviz_nbclust(customers_scaled, kmeans, method = "silhouette", nstart = 25)
```
* Suggests k = 5

```{r}
fviz_nbclust(customers_scaled, kmeans, method = "gap_stat", nstart = 25, k.max = 10)
```

* This says k = 1

* Hmm beginning to think the data is not suited to clustering


* I'll choose k = 3 from the elbow chart

#### K = 3

```{r}
customers_3k <- kmeans(customers_scaled, centers = 3, nstart = 25) 

customers_3k


```

```{r}
## repeating this using k = 2, produced very different clusters each time
## repeating with k = 3 gives the same/similar clusters each time

customers_scaled %>% 
  kmeans.ani(centers = 3)
```

```{r}
customers_with_3k_clusters <- augment(customers_3k, customers)
```
```{r}
customers_with_3k_clusters %>% 
  ggplot() +
  aes(x = annual_income_k, y = spending_score_1_100, shape = .cluster, colour = age) +
  geom_point() +
  scale_color_continuous(type = "viridis")

customers_with_3k_clusters %>% 
  ggplot() +
  aes(x = annual_income_k, y = spending_score_1_100, shape = .cluster, colour = sex) +
  geom_point()
```

* The clusters seems to be roughly equal male/female

* Cluster 1 = Higher annual income >= 75k, low spending score < 50, noone over 60

* Cluster 2 = Lower annual income <= 75, range of spending scores, seems to be 3 smaller clusters. Particualrly dense cluster earning between ~ 40 to 70k, with a spending score of 40 - 60 ish. Where most of the people over 65 years old, and also a lot of young people

* Cluster 3 = high earners, high spenders, all under 40


* lets try k = 5


##### k = 5

```{r}
customers_5k <- kmeans(customers_scaled, centers = 5, nstart = 25) 

customers_5k
```

```{r}
# gets same/similar clusters every time

customers_scaled %>% 
  kmeans.ani(centers = 5)
```

```{r}
customers_with_5k_clusters <- augment(customers_5k, customers)
```
```{r}
customers_with_5k_clusters %>% 
  ggplot() +
  aes(x = annual_income_k, y = spending_score_1_100, shape = .cluster, colour = age) +
  geom_point() +
  scale_color_continuous(type = "viridis")

customers_with_5k_clusters %>% 
  ggplot() +
  aes(x = annual_income_k, y = spending_score_1_100, shape = .cluster, colour = sex) +
  geom_point()
```

* Looks like 5 pretty distinct clusters. 


* Cluster 1 = low earner low spenders

* Cluster 2 = High earner low spender

* Cluster 3 = High earner high spender

* Cluster 4 = 50/50

* Cluster 5 = Low earner High spender


* I'd say the data seems well suited to clustering where k = 5.





















































