---
title: "MVP HW"
author: "Peter Menzies"
date: "28/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=F, warning=F}
library(infer)
library(janitor)
library(CodeClanData)
library(tidyverse)
```

```{r, message=F, warning=F}
sleep <- msleep %>% 
  clean_names()
summary(sleep)
```

# MVP 1.1

### Jabberwockies sleep comparison 

* $\alpha$ = 0.05
* $H_0$: sampled_animals_sleep = 7 hours
* $H_a$: sampled_animals_sleep != 7 hours

```{r}
observed_sleep_stat <- sleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))
observed_sleep_stat

null_sleep_dist <- sleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_sleep_dist %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_sleep_stat, direction = "both")

null_sleep_dist %>%  
  get_p_value(obs_stat = observed_sleep_stat, direction = "both")

```

* The p value is < 0.05, therefore we can reject the null hypothesis

* There is significant statistical evidence suggesting these animal's mean sleep total is different to that of the Jabberwocky

### Omnivores vs Herbivores

* $\alpha$ = 0.05
* $H_0$: mean_omnivore_sleep_total - mean_herbivore_sleep_total = 0
* $H_a$: mean_omnivore_sleep_total - mean_herbivore_sleep_total != 0

```{r}
omni_herbi_sleep <- sleep %>% 
  filter(vore == "omni" | vore == "herbi")

observed_omni_herbi_stat <- omni_herbi_sleep %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
observed_omni_herbi_stat

null_omni_herbi_dist <- omni_herbi_sleep %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_omni_herbi_dist %>% 
  visualise(bins = 30) + 
  shade_p_value(obs_stat = observed_omni_herbi_stat, direction = "both")

null_omni_herbi_dist %>%
  get_p_value(obs_stat = observed_omni_herbi_stat, direction = "both")
```

* p value > 0.05 therefore we fail to reject the Null Hypothesis

* There is not statistically significant evidence to suggest that omnivores and herbivores require different amounts of sleep. 

### Domesticated animals

* $\alpha$ = 0.05
* $H_0$: prop_domesticated = 0.05
* $H_a$: prop_domesticated > 0.05

```{r}
domesticated_animals <- sleep %>% 
  mutate(conservation = replace_na(conservation, "NA"),
    is_domesticated = as.logical(conservation == "domesticated"))

observed_domesticated_stat <- domesticated_animals %>% 
  filter(is_domesticated == T) %>% 
  summarise(prop_domesticated = n()/nrow(domesticated_animals))
observed_domesticated_stat

null_domesticated_dist <- domesticated_animals %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 10000, type = "simulate") %>% 
  calculate(stat = "prop")

null_domesticated_dist %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_domesticated_stat, direction = "right")

null_domesticated_dist %>% 
  get_p_value(obs_stat = observed_domesticated_stat, direction = "right")
```

* p < 0.05 therefore we can reject $H_0$

* There is statistically significant evidence suggesting more than 5% of the population of animals are domesticated.

# 1.2 Hypothesis testing
### 1.2.1 Defining hypotheis

###### 1 

* $H_0$: prop_aware_after_advertising = 0.04
* $H_a$: prop_aware_after_advertising > 0.04
* Null Hypothesis: The proportion of people aware of the coffee shop is unchanged at 40%
* Alternative Hypothesis: The proportion of people aware of the coffee shape is now greater than 40%

* Assumption: Initial survey results were statistically significant

* Generate Method: "simulate"

###### 2

* $H_0$: banner_top_CTR - banner_right_CTR = 0
* $H_a$: banner_top_CTR - banner_right_CTR > 0

* Null Hypothesis: The CTR of the newly positioned banner minus the CTR of the old position is equal to 0, and is therefore unchanged by the new position.

* Alternative Hypothesis: The CTR of the newly positioned banner minus the CTR of the old position is greater than 0, therefore showing an increase in CTR.

* Generate Method: "permute"


###### 3

* $H_0$: mean_width_mm != 145 
* $H_a$: mean_width_mm = 145 

* Null Hypothesis: The average width of the part is not 145 mm.

* Alternative Hypothesis: The average width of the part is 145 mm.

* Generate Method: "bootstrap"

# 1.2.2 Interpreting results

###### 1

* p value > 0.05 therefore failed to reject $H_0$

* There is not statistically significant evidence to suggest an increase in people's awareness of the coffee shop after the advertising effors.

###### 2

* p value < 0.01 therefore reject $H_0$

* There is statistically significant evidence suggesting an increase in CTR for the newly positioned banner.

###### 3

* p value > 0.05 therefore failed to reject $H_0$

* There is statistically significant evidence to suggest that the parts made in over this period of a week do not meet the required standards.




























