---
title: "Weekend Avocados"
author: "Peter Menzies"
date: "10/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MVP

```{r, message=F, warning=F}
source("data_exploration_cleaning.R")
```

##### Summary of data cleaning/featur engineering


PLU 4046 - small Hass
PLU 4225 - large Hass
PLU 4770 - Extra large Hass

* Convert Sizes into percentage of total sales

* Convert Bag numbers into percentage sold in small bags

* Convert Date into season
  -   Spring = March 1st - May 31st
  -   Summer = June 1st - August 31st
  -   Autumn = Sep 1st  - Nov 30th
  -   Winter = Dec 1st - Feb 28th

* Convert convential/organic into Organic - true false

* Regions - extract the regions which equal totalUS figures

* Convert year to factor


### 1st Predictor
```{r}
library(GGally)
library(modelr)
```

```{r}
alias_avocado <- lm(average_price ~ ., data = avocados_cleaned)

alias(alias_avocado)
```
* we can remove non_hass_percent

```{r}
avocados_cleaned <- avocados_cleaned %>% 
  select(-non_hass_percent)
```


```{r}
avocados_numeric <- avocados_cleaned %>% 
  select_if(is.numeric)

avocados_non_numeric <- avocados_cleaned %>% 
  select_if(function(x) !is.numeric(x))

avocados_non_numeric$average_price <- avocados_cleaned$average_price
```
```{r}
summary(prcomp(avocados_numeric, center = T, scale. = T))
```


* 5 principal components accounts for 96% of variance 
```{r}
ggpairs(avocados_numeric, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

* Biggest correlation = average_price ~ total_volume
* 2nd = average_price ~ small_hass_percentage 
* 3rd = average_price ~ xl_hass_percentage



```{r}
ggpairs(avocados_non_numeric, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

* Most movement to least (estimate): Organic, Region, season, year


* 1st predictors to test: total_volume, small_hass_percent, organic, region

```{r}
model_1a <- lm(average_price ~ total_volume, data = avocados_cleaned)
model_1b <- lm(average_price ~ small_hass_percent, data = avocados_cleaned)
model_1c <- lm(average_price ~ organic, data = avocados_cleaned)
model_1d <- lm(average_price ~ region, data = avocados_cleaned)
```

```{r}
summary(model_1a)
par(mfrow=c(2,2))
plot(model_1a)
```

```{r}
summary(model_1b)
par(mfrow=c(2,2))
plot(model_1b)
```

```{r}
summary(model_1c)
par(mfrow=c(2,2))
plot(model_1c)
```

```{r}
summary(model_1d)
par(mfrow=c(2,2))
plot(model_1d)
```

##### Average_price ~ total_volume 

* Multiple R^2 is highest = 0.5219
* Residual standard error is significant at 0.2418 (~ 25% of avg_price)
* Plots look ok, deviation at right tail of Q-Q plot, upwards trend in scale-location


# 2nd Predictor 

```{r}
avocados_resid <- avocados_cleaned %>% 
  add_residuals(model_1a) %>% 
  select(-average_price, -total_volume)
```

```{r}
ggpairs(avocados_resid, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

* remaining numeric correlations are pretty small: small_hass_percent is largest at 0.254
* boxplot movement most to least: region, year, season, organic

```{r}
model_2a <- lm(average_price ~ total_volume + small_hass_percent, data = avocados_cleaned)
model_2b <- lm(average_price ~ total_volume + region, data = avocados_cleaned)
model_2c <- lm(average_price ~ total_volume + year, data = avocados_cleaned)
model_2d <- lm(average_price ~ total_volume + season, data = avocados_cleaned)

```

```{r}
summary(model_2a)
par(mfrow=c(2,2))
plot(model_2a)
```

* R2 increase, resid standard error decrease

```{r}
summary(model_2b)
par(mfrow=c(2,2))
plot(model_2b)
```

```{r}
summary(model_2c)
par(mfrow=c(2,2))
plot(model_2c)
```

```{r}
summary(model_2d)
par(mfrow=c(2,2))
plot(model_2d)
```

##### average_price ~ total_volume + region (model_2b)

* Highest increase in R^2 (0.634) and highest drop in resid std error (0.2118)
* P values all significantly low
* Plots ok: Q-Q plot has deviation at right tail still

# 3rd predictor

```{r}
avocados_resid <- avocados_cleaned %>% 
  add_residuals(model_2b) %>% 
  select(-average_price, -total_volume, -region)
```
```{r}
ggpairs(avocados_resid, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

* Numeric correlations all very low
* Try season, year and organic and total_volume:region

```{r}
model_3a <- lm(average_price ~ total_volume + region + season, data = avocados_cleaned)
model_3b <- lm(average_price ~ total_volume + region + year, data = avocados_cleaned)
model_3c <- lm(average_price ~ total_volume + region + organic, data = avocados_cleaned)
model_3d <- lm(average_price ~ total_volume + region + total_volume:region, data = avocados_cleaned)

```

```{r}
summary(model_3a)
par(mfrow=c(2,2))
plot(model_3a)
```

```{r}
summary(model_3b)
par(mfrow=c(2,2))
plot(model_3b)
```

```{r}
summary(model_3c)
par(mfrow=c(2,2))
plot(model_3c)
```

```{r}
summary(model_3d)
par(mfrow=c(2,2))
plot(model_3d)
```

##### average_price ~ total_volume + region + season (model_3a)

* Highest Increase in multi R^2 (0.6835) and decrease in resid standard error (0.1971)
* All pvalues significantly low
* plots ok

# 4th Predictor

```{r}
avocados_resid <- avocados_cleaned %>% 
  add_residuals(model_2b) %>% 
  select(-average_price, -total_volume, -region, -season)
```
```{r}
ggpairs(avocados_resid, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

* Correlations are very low and not much movement in box plots other than year.
* Investigate interactions

##### Interactions
model_3a: average_price ~ total_volume + region + season

interactions:
* total_volume:region
* total_volume:season
* region:season 


```{r}
avocados_int_resid <- avocados_cleaned %>% 
  add_residuals(model_3a) %>% 
  select(-average_price)
```


```{r}
avocados_int_resid %>% 
  ggplot(aes(x = total_volume, y = resid, colour = region)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

avocados_int_resid %>% 
  ggplot(aes(x = total_volume, y = resid, colour = season)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

avocados_int_resid %>% 
  ggplot(aes(x = region, y = resid, colour = season)) +
  geom_boxplot() +
  geom_smooth(method = "lm", se = F)
```

```{r}
model_4a <- lm(average_price ~ total_volume + region + season + total_volume:region, data = avocados_cleaned)

model_4b <- lm(average_price ~ total_volume + region + season + total_volume:season, data = avocados_cleaned)

model_4c <- lm(average_price ~ total_volume + region + season + region:season, data = avocados_cleaned)

model_4d <- lm(average_price ~ total_volume + region + season + organic, data = avocados_cleaned)

model_4e <- lm(average_price ~ total_volume + region + season + year, data = avocados_cleaned)
```

```{r}
summary(model_4a)
par(mfrow=c(2,2))
plot(model_4a)
```

```{r}
summary(model_4b)
par(mfrow=c(2,2))
plot(model_4b)
```
```{r}
summary(model_4c)
par(mfrow=c(2,2))
plot(model_4c)
```

```{r}
summary(model_4d)
par(mfrow=c(2,2))
plot(model_4d)
```

```{r}
summary(model_4e)
par(mfrow=c(2,2))
plot(model_4e)
```

#####average_price ~ total_volume + region + season + year (model_4e)

* Highest increase in R^2 (0.7327) and reduction in resid std error (0.1812)
* all pvalues significant (year 2016 p = 0.048, so only just <0.05)
* plots look ok
* I am slightly dubious as to whether year should be included, because can it be used in predicting avocado price in 2021?

# 5th Predictor

```{r}
avocados_resid <- avocados_cleaned %>% 
  add_residuals(model_2b) %>% 
  select(-average_price, -total_volume, -region, -season, -year)
```
```{r}
ggpairs(avocados_resid, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

```{r}
model_5a <- lm(average_price ~ total_volume + region + season + year + organic, data = avocados_cleaned) 

model_5b <- lm(average_price ~ total_volume + region + season + year + total_volume:region, data = avocados_cleaned)

model_5c <- lm(average_price ~ total_volume + region + season + year + small_hass_percent, data = avocados_cleaned)

model_5d <- lm(average_price ~ total_volume + region + season + year + total_volume:season, data = avocados_cleaned)
```


```{r}
summary(model_5a)
par(mfrow=c(2,2))
plot(model_5a)
```

```{r}
summary(model_5b)
par(mfrow=c(2,2))
plot(model_5b)
```

```{r}
summary(model_5c)
par(mfrow=c(2,2))
plot(model_5c)
```


```{r}
summary(model_5d)
par(mfrow=c(2,2))
plot(model_5d)
```

##### average_price ~ total_volume + region + season + year + total_volume:region (model_5b)

```{r}
anova(model_4e, model_5b)
```
* It is significant despite some of the interactions having a high p value
* R squared now up to 0.7804 and res std error down to 0.1645

* drifting of both tails on Q-Q plot

#6th predictor

```{r}
model_6a <- lm(average_price ~ total_volume + region + season + year + total_volume:region + small_hass_percent, data = avocados_cleaned)

model_6b <- lm(average_price ~ total_volume + region + season + year + total_volume:region + organic, data = avocados_cleaned)

model_6c <- lm(average_price ~ total_volume + region + season + year + total_volume:region + total_volume:season, data = avocados_cleaned)
```

```{r}
summary(model_6a)
par(mfrow=c(2,2))
plot(model_6a)
```

```{r}
summary(model_6b)
par(mfrow=c(2,2))
plot(model_6b)
```

```{r}
summary(model_6c)
par(mfrow=c(2,2))
plot(model_6c)
```



* Needs further predictors added to achieve an acceptable R squared





