---
title: "Wk7d2 HW"
author: "Peter Menzies"
date: "01/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=F, warning=F}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
```

# MVP 
### 1

```{r}
bikes <- nyc_bikes %>% 
  mutate(year = year(start_time),
         month = month(start_time, label = T),
         date = date(start_time))

```

### 2

```{r}
bikes %>% 
  index_by(month) %>% 
  summarise(hire_count = n()) %>% 
  ggplot() +
  aes(x = month, y = hire_count) +
  geom_col()
```

* Probably not adequete for an accurate forecast, I'd prefer to have more than one years worth of data to do that

* However it does give a decent impression of the trend that more bikes are hired in the Summer months than over Winter.

###3

```{r}
bikes_date_count <- bikes %>% 
  index_by(date) %>% 
  summarise(hire_count = n())

bikes_date_count %>% 
  ggplot() +
  aes(x = date, y = hire_count) +
  geom_line() +
  scale_x_date(breaks = "1 month",
                   labels = month,
                   date_labels = "%B") +
  theme(axis.text.x = element_text(angle = 30, vjust = 0.7))
```

* Similar trend of increased hires in Summer
* Shows there is significant variation in hire numbers within each month, perhaps cyclical with each week.

* More data points so probably better for forecasting but I would still prefer to have multiple years of data.


### 4

```{r}
bikes_filled <- bikes_date_count %>% 
  fill_gaps(hire_count = 0)

# 0 chosen as I assume there were no hires on these dates and that is why they were not included. Using the median I feel would falsely inflate the hire count.

model <- bikes_filled %>% 
  model(
    mean_model = MEAN(hire_count),
    naive_model = NAIVE(hire_count),
    snaive_model = SNAIVE(hire_count),
    arima_model = ARIMA(hire_count)
  )
```

### 5

```{r}
forecast_mean <- model %>% 
  select(mean_model) %>% 
  forecast(h = 120)

forecast_mean %>% 
  autoplot(bikes_filled) +
  scale_x_date(breaks = "1 month",
                   date_labels = "%B %y") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.1))
```


```{r}
forecast_naive <- model %>% 
  select(naive_model) %>% 
  forecast(h = 120)

forecast_naive %>% 
  autoplot(bikes_filled) +
  scale_x_date(breaks = "1 month",
                   date_labels = "%B %y") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.1))
```

```{r}
forecast_snaive <- model %>% 
  select(snaive_model) %>% 
  forecast(h = 120)

forecast_snaive %>% 
  autoplot(bikes_filled) +
  scale_x_date(breaks = "1 month",
                   date_labels = "%B %y") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.1))
```

```{r}
forecast_arima <- model %>% 
  select(arima_model) %>% 
  forecast(h = 120)

forecast_arima %>% 
  autoplot(bikes_filled) +
  scale_x_date(breaks = "1 month",
                   date_labels = "%B %y") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.1))
```

* SNAIVE seems like the bet model, as it takes into account daily variation but I don't think any are showing the expected increase in hires as it gets to April and May

### 6

```{r}
train <- bikes_filled %>% 
  filter_index("2018-01-01" ~ "2018-09-30")

model_train <- train %>%    # choo choo
  model(
    mean_model = MEAN(hire_count),
    naive_model = NAIVE(hire_count),
    snaive_model = SNAIVE(hire_count),
    arima_model = ARIMA(hire_count)
  )

forecast_train <- model_train %>% 
  forecast(h = 120)
```
```{r}
forecast_train %>% 
  autoplot(train) +
  autolayer(filter_index(bikes_filled, "2018-10-01" ~ .), colour = "black") +
  scale_x_date(breaks = "1 month",
                   date_labels = "%B %y") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.1)) 

accuracy(forecast_train, bikes_filled)
```


### 7

* SNAIVE seems the most accurate.

* I'd want another year at least to model the data on.
* The SNAIVE model is perhaps acceptable for the first 3 months of 2019.

### 8 

```{r}
bikes %>% 
  ggplot() +
  geom_point(aes(x = start_lat, y = start_long, colour = month), position = "jitter") +
  facet_wrap(~ bike_id)
```

* Bikes 31681 & 31735 were used the most in January to April.
* Bikes 33074, 33557 and 33571 were used most in June, July and August.
* The remaining bikes were used the most from Oct to December.

```{r}
bikes %>% 
  ggplot() +
  geom_point(aes(x = end_lat, y = end_long, colour = month), position = "jitter") +
  facet_wrap(~ bike_id)
```

* Seems a wider variety of starting points  and more clustering of end points


### 9 

```{r}
library(leaflet)
leaflet(bikes) %>% 
  addTiles() %>% 
  addMarkers(lng = bikes$start_long, lat = bikes$start_lat, clusterOptions = markerClusterOptions(), clusterId = "start point") #%>% 
  #addMarkers(lng = bikes$end_long, lat = bikes$end_lat, clusterOptions = markerClusterOptions(), clusterId = "end point")
  
```










