---
title: "manual model dev hw"
author: "Peter Menzies"
date: "07/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MVP
```{r, message=F, warning=F}
library(tidyverse)
library(GGally)
library(modelr)
```
```{r}
houses <- read_csv("data/kc_house_data.csv")
```

```{r}
head(houses)
summary(houses)
```

```{r}
houses_trim <- houses %>% 
  select(-sqft_living15, -sqft_lot15, -id, -zipcode, -date) %>% 
  mutate(waterfront = as.logical(waterfront),
         renovated = if_else(yr_renovated == 0, F, T)) %>% 
  select(-yr_renovated)
  
```

* grade and condition are ordinal variables

```{r}
alias_model <- lm(price ~ ., data = houses_trim)
alias(alias_model)

```
* we can remove sqft_basement 

```{r}
houses_trim <- houses_trim %>% 
  select(-sqft_basement)
```


```{r}
houses_trim_numeric <- houses_trim %>%
  select_if(is.numeric)

houses_trim_nonnumeric <- houses_trim %>%
  select_if(function(x) !is.numeric(x))

houses_trim_nonnumeric$price <- houses_trim$price

ggpairs(houses_trim_numeric, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```


highest correlations: 
* price ~ sqft_living  = 0.702
* price ~ grade  = 0.667
* price~ sqft_above  = 0.606



```{r}
ggpairs(houses_trim_nonnumeric, upper = list(continuous = wrap("cor", family="sans", size = 2)))
```
* Price ~ waterfront has a lot of movement between box plots so maybe also worth considering


```{r}
houses_pca <- prcomp(houses_trim_numeric, center = T, scale. = T)
summary(houses_pca)
houses_pca$rotation
```

* Needs 8 principal components to account for 90% of variance


## First Predictor

```{r}
mod1a <- lm(price ~ sqft_living, data = houses_trim)

summary(mod1a)

par(mfrow = c(2,2))
plot(mod1a)
```

```{r}
mod1b <- lm(price ~ sqft_above, data = houses_trim)

summary(mod1b)

par(mfrow = c(2,2))
plot(mod1b)
```

```{r}
mod1c <- lm(price ~ grade, data = houses_trim)

summary(mod1c)

par(mfrow = c(2,2))
plot(mod1c)
```


```{r}
mod1d <- lm(price ~ waterfront, data = houses_trim)

summary(mod1d)

par(mfrow = c(2,2))
plot(mod1d)
```
* All have good p values

* mod1a (price ~ sqft_living) has highest R squared so I'll use it 1st, though the scale-location graph has a worrying upwards trend.

## Second predictor

```{r}
houses_resid <- houses_trim %>% 
  add_residuals(mod1a) %>% 
  select(-price, sqft_living)
```
```{r}
houses_resid %>% 
  ggpairs(upper = list(continuous = wrap("cor", family="sans", size = 2)))
```

* Highest Correlations with resid are "lat", "long", "yr_built"
* Also a lot of movement in "waterfront" boxplot
* So those 4 would be in my choices for next predictor to add

