---
title: "Wk6 D2 hw"
author: "Peter Menzies"
date: "24/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=F}
library(tidyverse)
library(janitor)
```


# MVP 

```{r, message=F}
phones <- read_csv("data/20190928-items.csv") %>% 
  clean_names()
head(phones)
summary(phones)
```
```{r, message=F}
phones %>% 
  group_by(brand) %>% 
  summarise(total_models = n()) %>% 
  arrange(desc(total_models))
```
* Samsungs have most phones in dataset with 397.

```{r}
samsung_stats <- phones %>% 
  filter(brand == "Samsung") %>% 
  summarise(num_phones = n(),
            mean_rating = mean(rating),
            sd_rating = sd(rating))

phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot() +
  aes(x = rating) +
  geom_histogram(aes(y = ..density..), colour = "white", bins = 40) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_stats$mean_rating,
      sd = samsung_stats$sd_rating
    ),
    colour = "orange"
  )



```

* I'd say the normal distribution fits quite well, other than the significant amount of outliers at 1 and 5 that do not fit. The data is skewed to the left.

```{r}
phones %>% 
  filter(brand == "Samsung") %>% 
  filter(rating <= (samsung_stats$mean_rating + samsung_stats$sd_rating),
         rating >= (samsung_stats$mean_rating - samsung_stats$sd_rating)) %>% 
  summarise(one_sd_ratings_prop = n()/samsung_stats$num_phones)

phones %>% 
  filter(brand == "Samsung") %>% 
  filter(rating <= (samsung_stats$mean_rating + samsung_stats$sd_rating * 2),
         rating >= (samsung_stats$mean_rating - samsung_stats$sd_rating * 2)) %>% 
  summarise(two_sd_ratings = n()/samsung_stats$num_phones)

phones %>% 
  filter(brand == "Samsung") %>% 
  filter(rating <= (samsung_stats$mean_rating + samsung_stats$sd_rating * 3),
         rating >= (samsung_stats$mean_rating - samsung_stats$sd_rating * 3)) %>% 
  summarise(three_sd_ratings = n()/samsung_stats$num_phones)
```

* This doesn't fit with the empirical 3 sigma rule. Each quantile contains a lower proportion of the ratings than expected. Due to the high number of outlier ratings of 1 and 5 I assume. 


*[Post Discussion] - Woops the 1st quantile (+/- one sd) contains a higher proportion of results than would be predicted by the empirical rule

# EXT

```{r}
samsung_ratings <- phones %>% 
  filter(brand == "Samsung")

qqnorm(y = samsung_ratings$rating)
```

Not entirely sure what I'm looking at but it's different to a normal qq distribution. Looks like a lot data points at the extremes, which I suppose fits with the high density of outliers in the earlier plot?