---
title: "Week 6 Day 3 HW"
author: "Peter Menzies"
date: "25/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=F}
library(tidyverse)
library(janitor)
library(infer)
```

# MVP

```{r, message=F, warning=F}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
```

```{r}
ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram(aes(y = ..density..), colour = "white", bins = 50) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = mean(ames$lot_area),
      sd = sd(ames$lot_area)
    ),
    colour = "orange"
  )

ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_boxplot()

qqnorm(y = ames$lot_area)
```

I'd say that is not normally distributed. There is a high density of results below 30,000 which look to have a normal distribution but there are also a significant number of results with a far greater lot area, which affect the distribution.


```{r}
bootstrapped_lot_area <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")


ci_95 <- bootstrapped_lot_area %>% 
  get_ci(level = 0.95, type = "percentile")

bootstrapped_lot_area %>% 
  visualise() +
  shade_ci(endpoints = ci_95)
```

```{r}
ci_99 <- bootstrapped_lot_area %>% 
  get_ci(level = 0.99, type = "percentile")

bootstrapped_lot_area %>% 
  visualise() +
  shade_ci(endpoints = ci_99)
```

This is wider, which is to be expected.

```{r}
bootstrapped_lot_area %>% 
  summarise(point_estimate_mean_lot_area = mean(stat))
```

# EXT

```{r}
ames_year_built <- ames %>% 
  select(order, year_built) %>% 
  mutate(before_1920 = as.numeric(year_built < 1920)) 
```

```{r}
bootstrapped_year_200 <- ames_year_built %>% 
  specify(response = before_1920) %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrapped_year_5000 <- ames_year_built %>% 
  specify(response = before_1920) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrapped_year_50000 <- ames_year_built %>% 
  specify(response = before_1920) %>% 
  generate(reps = 50000, type = "bootstrap") %>% 
  calculate(stat = "mean")

```


```{r}
bootstrapped_year_200 %>% 
  summarise(point_estimate = mean(stat)) 
bootstrapped_year_200 %>% 
  get_ci(level = 0.95, type = "percentile")
            
```
```{r}
bootstrapped_year_5000 %>% 
  summarise(point_estimate = mean(stat)) 
bootstrapped_year_5000 %>% 
  get_ci(level = 0.95, type = "percentile")
```

```{r}
bootstrapped_year_50000 %>% 
  summarise(point_estimate = mean(stat)) 
bootstrapped_year_50000 %>% 
  get_ci(level = 0.95, type = "percentile")
```

Number of reps seems to make very little difference to the point estimate and confidence intervals. 

I assume there comes a point where the original sample size is the limiting factor so increasing the number of bootstrap samples will make no difference.


```{r}
bootstrapped_year_10 <- ames_year_built %>% 
  specify(response = before_1920) %>% 
  generate(reps = 10, type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrapped_year_10 %>% 
  summarise(point_estimate = mean(stat)) 
bootstrapped_year_10 %>% 
  get_ci(level = 0.95, type = "percentile")
```












