---
title: "WK7 D1 HW"
author: "Peter Menzies"
date: "30/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=F, warning=F}
library(dplyr)
library(lubridate)
library(tidyverse)
library(tsibble)
library(tsibbledata)
library(feasts)

date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")

library(nycflights13)
```

# 1 Dates and Times
### 1.1

```{r}
year(date1)
month(date1, label = T, abbr = F)
mday(date1)
yday(date1)
wday(date1)
```

### 1.2

```{r}
next_fortnight <- date1 + weeks(2)
next_fortnight

previous_decade <- date2 - years(10)
previous_decade
```

### 1.3

```{r}
this_year <- today()
this_year
  
interval_years <- lubridate::interval(previous_decade, this_year)
interval_years
```

### 1.4

```{r}
nyc_date1 <- with_tz(date1, tzone = "America/New_York")
nyc_date1

nyc_date2 <- with_tz(date2, tzone = "America/New_York")
nyc_date2
```

### 1.5

```{r}
flights %>% 
  mutate(departure_date = make_datetime(year, month, day, hour, minute)) 
```

# Time Series Familiarity
### 2.6

```{r}
weather_selected <- weather %>% 
  select(time_hour, origin, temp, dewp, humid, precip)

head(weather_selected) 
```

* Hourly observations from 1st Jan 2013 to 30th Dec 2013, taken at Newark Liberty International Airport, John F. Kennedy International Airport and LaGuardia Airport.


### 2.7

```{r}
weather_tsibble <- weather_selected %>% 
  as_tsibble(key = origin, index = time_hour)
weather_tsibble
```
### 2.8

```{r}
weather_tsibble <- weather_tsibble %>% 
  mutate(year = year(time_hour),
         month = month(time_hour, label = T))
weather_tsibble

weather_tsibble %>% 
  ggplot() +
  aes(x = time_hour, y = temp, colour = origin) +
  geom_line( show.legend = F) +
  facet_wrap(~ origin, ncol = 1) +
  labs(x = "Time",
       y = "Temperature ºF",
       title = "Temperature at New York Airports in 2013") +
  scale_x_datetime(breaks = "1 month",
                   labels = month,
                   date_labels = "%B") +
  theme(axis.text.x = element_text(angle = 30, vjust = 0.7),
        plot.title = element_text(face = "bold", hjust = 0.4))
  
```

* Plotting the whole timeseries gives a good impression of the overall trend in temperature throughout the year, and shows that genereally temperatures are similar across the 3 airports.


* However it isn't clear how the temperatures vary across a month, week or day. Depending on what interests us perhaps limit the timeframe of the plot or use a rolling window average.

### 2.9

```{r, message=F}
library(slider)
weather_tsibble %>% 
  mutate(avg_roll_temp = slide_dbl(
    .x = temp,
    .f = ~ mean(., na.rm = T),
    .before = 84,
    .after = 84
  )) %>% 
  ggplot() +
  aes(x = time_hour, colour = origin) +
  geom_line(aes(y=temp), colour = "grey") +
  geom_line(aes(y=avg_roll_temp), show.legend = F) +
  facet_wrap(~ origin, ncol = 1) +
  labs(x = "Time",
       y = "Temperature ºF",
       title = "Temperature at New York Airports in 2013") +
  scale_x_datetime(breaks = "1 month",
                   labels = month,
                   date_labels = "%B") +
  theme(axis.text.x = element_text(angle = 30, vjust = 0.7),
        plot.title = element_text(face = "bold", hjust = 0.4))
                 
```

* Window of 84 hours (3.5 days) before and after the point was chosen so that the rolling average was of a week's temperature. Chosen the variation in a smaller window is difficult see on a grid of the whole year. 

* The temperature trends upwards from February to July then trends downwards till December as one might expect. There's a reasonable amount of cyclical variation within each month.

### 2.10

```{r}
weather_tsibble_day <- weather_tsibble %>% 
  mutate(avg_day_temp = slide_dbl(
    .x = temp,
    .f = ~ mean(., na.rm = T),
    .before = 12,
    .after = 12,
    .step = 24
  ))

weather_tsibble_day %>% 
  drop_na(avg_day_temp) %>% 
  ggplot() +
  aes(x = time_hour, colour = origin) +
  geom_line(aes(y = avg_day_temp), show.legend = F) +
  facet_wrap(~ origin, ncol = 1) +
  labs(x = "Time",
       y = "Temperature ºF",
       title = "Temperature at New York Airports in 2013") +
  scale_x_datetime(breaks = "1 month",
                   labels = month,
                   date_labels = "%B") +
  theme(axis.text.x = element_text(angle = 30, vjust = 0.7),
        plot.title = element_text(face = "bold", hjust = 0.4))
```



