---
title: "Week 11 Day 2 Decision trees"
author: "Peter Menzies"
date: "12/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, warning=F, message=F}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(yardstick)
library(modelr)
```
```{r}
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```


# MVP

### 1

```{r}
titanic_clean <- titanic_set %>% 
  drop_na(survived) %>% 
  mutate(sex = as.factor(sex),
         survived = factor(survived, 
                              levels = c(0,1), 
                              labels = c("No", "Yes")),
         pclass = factor(pclass, 
                            levels = c(3,2,1), 
                            labels = c("Lower", "Middle", "Upper")),
         embarked = as.factor(embarked),
         age_status = as.factor(if_else(age >= 16, "adult", "child"))) %>% 
  select(-X1, -passenger_id, -name, -ticket, -fare, -cabin, -age) %>% 
  drop_na()
    
### POST-DISCUSSION: I should have dropped NA's after selecting, this is going to affect the trees significantly
  

summary(titanic_clean)
```

### 2

```{r}
library(GGally)
ggpairs(titanic_clean)
```
Useful variables:

*   Sex
*   embarked
*   age status
*   class

### 3

```{r}
nrow_titanic <- nrow(titanic_clean)

test_index <- sample(1:nrow_titanic, size = nrow_titanic*0.2)
```
```{r}
test_titanic <- slice(titanic_clean, test_index)
train_titanic <- slice(titanic_clean, -test_index)
```
* Chose an 80/20 split 

```{r}
test_titanic %>% 
janitor::tabyl(survived)

train_titanic %>% 
  janitor::tabyl(survived)
```

* They are reasonably balanced

### 4

```{r}
titanic_tree <- rpart(survived ~ .,
                      data = train_titanic,
                      method = "class")
```

```{r}
rpart.plot(titanic_tree, 
           yesno = 2, 
           fallen.leaves = T, 
           faclen = 6, 
           digits = 4, 
           type = 4, 
           extra = 101)
```

### 5

1st variable: Sex 
        -   splits the data 50/50
        -   70/74 women survived = higher survival chance
        -   29/73 Men survived

2nd variable (splits Males): Class
        -   small number lower/middle class -> 6/10 survived = higher survival chance
        -   23/63 upper class survived 
        
3rd variable (splits Upper Class): Port of embarkation
        -   39 for ports Q and S -> 11/39 survived
        -   24 for port C -> 12/24 survived = higher survival chance
        
4th variable (splits port C): Sibling/parents on board
        -  16 for 0 sibs/parents = 7/16 survived
        -   8 for >= 1 sib/parents = 5/8 survived = higher survival chance

* Sex is the strongest predictor

* Highest chance of survival are women. 

* Lowest chance is a man, in upper class, who boarded at Queenstown or Southampton

### 6

```{r}
titanic_test_pred <- test_titanic %>% 
  add_predictions(titanic_tree, type = "class")
```

```{r}
 conf_mat <- titanic_test_pred %>% 
  conf_mat(truth = survived, estimate = pred)

conf_mat
```

* High number for False Negatives

```{r}
titanic_test_pred %>%
  sensitivity(truth = survived, estimate = pred)

titanic_test_pred %>%
  specificity(truth = survived, estimate = pred)
```

* Decent sensitivity (True Positive Rate)
* Poor specificity (True Negative Rate)

# Extension

```{r}
titanic_tree2 <- rpart(survived ~ .,
                      data = train_titanic,
                      method = "class",
                      control = rpart.control(
                        minsplit = 2,
                        minbucket = 1))
```

```{r}
rpart.plot(titanic_tree2, 
           yesno = 2, 
           fallen.leaves = T, 
           faclen = 6, 
           digits = 4, 
           type = 4, 
           extra = 101)
```

```{r}
titanic_test_pred2 <- test_titanic %>% 
  add_predictions(titanic_tree2, type = "class")
```

```{r}
 conf_mat2 <- titanic_test_pred2 %>% 
  conf_mat(truth = survived, estimate = pred)

conf_mat2
```


```{r}
titanic_test_pred2 %>%
  sensitivity(truth = survived, estimate = pred)

titanic_test_pred2 %>%
  specificity(truth = survived, estimate = pred)
```
* Adds in Age status to splits males = yes
* Adds in number of parents to split siblings/spouses >= 1

* Similar TPP (sensitivity) and TNP (specificity) to original model



#### 3rd model
```{r}
titanic_tree3 <- rpart(survived ~ .,
                      data = train_titanic,
                      method = "class",
                      control = rpart.control(
                        minsplit = 30,
                        minbucket = 15))
```

```{r}
rpart.plot(titanic_tree3, 
           yesno = 2, 
           fallen.leaves = T, 
           faclen = 6, 
           digits = 4, 
           type = 4, 
           extra = 101)
```

```{r}
titanic_test_pred3 <- test_titanic %>% 
  add_predictions(titanic_tree3, type = "class")
```

```{r}
 conf_mat3 <- titanic_test_pred3 %>% 
  conf_mat(truth = survived, estimate = pred)

conf_mat3
```


```{r}
titanic_test_pred3 %>%
  sensitivity(truth = survived, estimate = pred)

titanic_test_pred3 %>%
  specificity(truth = survived, estimate = pred)
```

* stops after 1 split
* Higher Sensitivity (TPP), lower specificity (TNP)


#### 4th model
```{r}
titanic_tree4 <- rpart(survived ~ .,
                      data = train_titanic,
                      method = "class",
                      control = rpart.control(
                        minsplit = 15,
                        minbucket = 9,
                        maxdepth = 30))
```

```{r}
rpart.plot(titanic_tree4, 
           yesno = 2, 
           fallen.leaves = T, 
           faclen = 6, 
           digits = 4, 
           type = 4, 
           extra = 101)
```

```{r}
titanic_test_pred4 <- test_titanic %>% 
  add_predictions(titanic_tree3, type = "class")
```

```{r}
 conf_mat4 <- titanic_test_pred4 %>% 
  conf_mat(truth = survived, estimate = pred)

conf_mat4
```


```{r}
titanic_test_pred4 %>%
  sensitivity(truth = survived, estimate = pred)

titanic_test_pred4 %>%
  specificity(truth = survived, estimate = pred)
```

* Splits Males to still high sens low spec



