---
title: "Week 5 Day 2 HW"
author: "Peter Menzies"
date: "17/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=FALSE}
library(tidyverse)
library(CodeClanData)
library(scales)

```

```{r, message=F}
revenue_breakdown <- qb_revenue_breakdown
monthly_sales_qb <- qb_monthly_sales
competitors <-  qb_competitors
device_data <-qb_device_data

col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```

# MVP 1&2

#1.1
```{r}
revenue_breakdown %>% 
  ggplot() +
  aes(x = Product, y = Revenue, fill = Year) +
  geom_col() +
  labs(y = "Revenue (pounds)", title = "Revenue Breakdown") +
  theme(axis.text.x = element_text(angle = 40, vjust = 0.7),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(alpha(colour = "gray", 0.3)),
        plot.title = element_text(hjust = 0.5, size = 16)) +
  scale_fill_discrete(type = col_scheme)
  
```


* Revenue improved for all products in 2019, especially from Subscription Services.

# 1.2

```{r}
monthly_sales_qb %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  aes(x = Date, y = Amount) +
  geom_line() +
  geom_point() +
  labs(y = "Sales (pounds)", title = "Sales of Kwikbit Unit 1") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(alpha(colour = "gray", 0.3)),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_discrete(type = col_scheme)
```



* Sales are increasing! There was a particularly good month in Feb 2019

# 1.3

```{r}
monthly_sales_qb %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales", 
         str_detect(Date, "2019")) %>% 
  ggplot() +
  aes(x = Date, y = Amount, group = Cashflow, colour = Cashflow) +
  geom_line() +
  geom_point() +
  labs(x = "Month", title = "Revenue and Costs in 2019") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(alpha(colour = "gray", 0.3)),
        plot.title = element_text(hjust = 0.5, size = 16)) +
  scale_colour_discrete(type = col_scheme)
```


* While Total Revenue fluctuates monthly it remains much higher than monthly costs, which are pretty constant.

# 1.4
```{r}
competitors %>% 
  filter(Revenue != 0) %>% 
  mutate(revenue_millions = Revenue/1000000) %>% 
  ggplot() +
  aes(x = Year, y = revenue_millions, fill = Company) +
  geom_area() +
  labs(y = "Revenue (millions)", title = "Revenue of Competitors") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(alpha(colour = "gray", 0.3)),
        plot.title = element_text(hjust = 0.5, size = 16)) +
  scale_fill_discrete(type = col_scheme)
  
```


* Competitor 1 has the largest total revenue and the largest increase in revenue over the 5 years.
* All competitors are increasing their revenue each year.


# 1.5

```{r}
competitors %>% 
  filter(Revenue != 0) %>% 
  mutate(revenue_millions = Revenue/1000000) %>% 
  ggplot() +
  aes(x = Year, y = revenue_millions, colour = Company) +
  geom_line() +
  geom_point() +
  labs(y = "Revenue (millions)", title = "Revenue of Competitors") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(alpha(colour = "gray", 0.3)),
        plot.title = element_text(hjust = 0.5, size = 16)) +
  scale_colour_discrete(type = col_scheme)


```


* This graph makes it clearer that competitor 3 started with more revenue than competitor 2, but was overtaken in 2019.

* Slightly problematic that it implies Competitor 3 had 0 revenue in 2015 when in fact it was 3000 (0.003 on this scale, and I suppose pretty much 0 with the numbers we're talking about)

# 1.6

```{r}
device_data %>% 
  group_by(device, id) %>% 
  mutate(total_mins = hours*60 + mins,
         running_total_thousands = cumsum(counts)/1000,
         device = recode(device,
                         "competitor1" = "Comp1",
                         "competitor2" = "Comp2",
                         "competitor3" = "Comp3")) %>% 
  ggplot() +
  aes(x = total_mins, y = running_total_thousands, colour = device) +
  geom_line() +
  facet_grid(device ~ id) +
  labs(x = "Time (mins)", y = "Steps (thousands)", title = "Total steps per person per device") +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 40, vjust = 0.7),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(alpha(colour = "gray", 0.3)),
        plot.title = element_text(hjust = 0.5, size = 16))+
  scale_colour_discrete(type = col_scheme)


```


* Looks like all devices count a similar number of steps, which I suppose is the aim. 











