---
title: "week 10 day 2 HW"
author: "Peter Menzies"
date: "06/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=F, warning=F}
library(tidyverse)
```

# MVP
#### 1

```{r}
diamonds_data <- read_csv("diamonds.csv")

head(diamonds_data)
summary(diamonds_data)
```

#### 2

```{r}
library(GGally)

diamonds_data %>% 
  select(carat, x, y, z) %>% 
  ggpairs()

```

#### 3

```{r}
diamonds_working <- diamonds_data %>% 
  select(-x, -y, -z, -X1)
```

#### 4
###### i

```{r}
ggpairs(diamonds_working)
```

##### ii

```{r}
diamonds_working %>% 
  ggplot() +
  aes(x = carat, y = price) +
  geom_point()
```
* Clear positive correlation


#### 5

##### i

```{r}
unique(diamonds_working$cut)
unique(diamonds_working$clarity)
unique(diamonds_working$color)
```

* cut = 4 Dummy variables

* clarity = 7 Dummy variables

* Colour = 6 Dummy variables

##### ii

```{r}
library(fastDummies)
```
```{r}
dummy_cols(diamonds_working, select_columns = c("cut", "clarity", "color"), remove_first_dummy = T, remove_selected_columns = T)
```
 
* Correct number of dummy columns

#### 6
```{r}
library(broom)
library(ggfortify)
```

##### i
```{r}
model_diamonds1 <- lm(price ~ carat, data = diamonds_working)

summary(model_diamonds1)
autoplot(model_diamonds1)
```
* Low p value, High R squared = good stuff

* Res vs fitted = line rises to the right, not good
* Q-Q = looks odd
* Scale-location = line rises to right, not good

##### ii

```{r}
model_diamonds2 <- lm(log(price) ~ carat, data = diamonds_working)

summary(model_diamonds2)
autoplot(model_diamonds2)
```

* p value and r squared still good
* graphs look worse!

```{r}
model_diamonds3 <- lm(price ~ log(carat), data = diamonds_working)

summary(model_diamonds3)
autoplot(model_diamonds3)
```

* p value and r squared still good
* graphs look worse!
```{r}
model_diamonds4 <- lm(log(price) ~ log(carat), data = diamonds_working)

summary(model_diamonds4)
autoplot(model_diamonds4)
```

* BOTH LOGS
* P value and R squared even better

* Graphs look perfect

##### iii

```{r}
model_diamonds5 <- lm(log(price) ~ log(carat) + cut, data = diamonds_working)

summary(model_diamonds5)
autoplot(model_diamonds5)
```

```{r}
model_diamonds6 <- lm(log(price) ~ log(carat) + clarity, data = diamonds_working)

summary(model_diamonds6)
autoplot(model_diamonds6)
```

```{r}
model_diamonds7 <- lm(log(price) ~ log(carat) + color, data = diamonds_working)

summary(model_diamonds7)
autoplot(model_diamonds7)
```


* ALl look good graph wise
* All have low p values and high r squared values
* Clarity has the highest R Squared value so is the best categorical predictor

##### iv
* Clarity
* reference level = clarity I1 (#changed after hw discussion)
* Clarity of "IF" shows greatest difference (increase) in price from reference level. Makes sense since it is the "best" clarity

(post discussion)
* exp of IF coefficient gives actual coefficient
```{r}
exp(1.114625)
```
* Assuming carat is constant, if the clarity is changed from I1 to IF the diamond will be 3 times as expensive


# Extension

#### 7

```{r}
model_diamonds8 <- lm(log(price) ~ log(carat) + clarity + log(carat):clarity, data = diamonds_working)

summary(model_diamonds8)
autoplot(model_diamonds8)
```

* Yes it is statistically justified
* It also makes sense that a diamond that has a better clarity and a has more carrots will have a higher price.

* Only slightly improves r squared so not really the correct way of approacing the model. We'll use anova() in the future


##### 8

```{r}
coplot(log(price) ~ log(carat)|clarity, 
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = diamonds_working)
```

* This shows that as log(carat) increases, the log(price) increases for all clarities.

* Perhaps shows that the carat doesn't have to be as high for the price to be high for the better clarities.

```{r}
# Post discussion
diamonds_working %>%
  ggplot(aes(x = log(carat), y = log(price), colour = clarity)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ clarity)
```

