---
title: "HW - Linear Regression"
author: "Peter Menzies"
date: "05/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=F, warning=F}
library(tidyverse)
library(modelr)
library(broom)
```

# MVP

#### 1
```{r}
project <- read_csv("data/project_management.csv")
```


#### 2
```{r}
project %>% 
  ggplot(aes(x = actual_length, y = estimated_length)) +
  geom_point()
```


#### 3
```{r}
project %>% 
  summarise(cor = cor(estimated_length, actual_length))
```
* Indicates a strong positive correlation 

#### 4

```{r}
model_project <- lm(formula = estimated_length ~ actual_length, data = project)
model_project
```
#### 5

```{r}
tidy(model_project)
glance(model_project)
```
y = 0.52x + 4.587

* slope = 0.52...
* Positive gradient, for every increase of 1 for x there is an increase of 0.5 for y 

* R^2 = 0.647...
* Quite High, 64% of the variation in estimated_length can be explained by variation in actual_length

#### 6

```{r}
model_project %>% 
  autoplot()
```

* Graphs look fine to me other than the outliers
* p value < 0.005 so the correlation is statistically significant

# Extension

```{r}
project %>% 
  ggplot(aes(x = actual_length, y = estimated_length)) +
  geom_point() +
  geom_text(aes(label = 1:nrow(project)))


```

outliers - 16, 5, 36, 31







