---
title: "Meteorite Analysis"
output: html_document
---
# Read in cleaned Meteorite Data
```{r}
source("cleaning_script.R")
```

# Analysis

# Largest Meteorites

```{r}
meteorite_landings_cleaned %>% 
  slice_max(mass_g, n = 10) %>% 
  select(name, year, mass_g)
```

# Average mass for falling vs found meteorites

```{r}
meteorite_landings_cleaned %>% 
  group_by(fall) %>% 
  summarise(mean_mass_g = mean(mass_g))
```

# Number of meteorites per year since 2000

```{r}
meteorite_landings_cleaned %>% 
  filter(year >= 2000) %>% 
  group_by(year) %>% 
  summarise(total_meteorites = length(id))

```

# Meteorites by latitude

```{r}
meteorite_landings_cleaned %>% 
  filter(latitude > 0) %>% 
  summarise(northern_hemisphere_meteorites = length(id),
            mean_size = mean(mass_g))

meteorite_landings_cleaned %>% 
  filter(latitude < 0) %>% 
  summarise(southern_hemisphere_meteorites = length(id),
            mean_size = mean(mass_g))

# unable to determine meteorites falling directly on the equator due to coercing "0" of NA's 

meteorite_landings_cleaned %>% 
  filter(latitude != 0 & latitude <= abs(23.5)) %>%           # to remove coerced 0 values
  summarise(meteorites_between_tropics = length(id),
            mean_size = mean(mass_g))

meteorite_landings_cleaned %>% 
  filter(latitude > 23.5) %>% 
  summarise(meteorites_north_of_cancer = length(id),
            mean_size = mean(mass_g))

meteorite_landings_cleaned %>% 
  filter(latitude < -23.5) %>% 
  summarise(meteorites_south_of_capricorn = length(id),
            mean_size = mean(mass_g))

meteorite_landings_cleaned %>% 
  filter(latitude > 66.5) %>% 
  summarise(meteorites_arctic_circle = length(id),
            mean_size = mean(mass_g))

meteorite_landings_cleaned %>% 
  filter(latitude < -66.5) %>% 
  summarise(meteorites_antarctic_circle = length(id),
            mean_size = mean(mass_g))
```
* Conclusions
    -   Far more meteorite landings reported in the Northern Hemisphere
    -   Mean size of the Southern Hemisphere landings is approximately double that of Northern Hemisphere landings
    -   Over 50% of Southern Hemisphere reported landings were in the Antarctic Circle
    -   ~0.5% of Northern Hemisphere reported landings in Arctic Circle
    -   Mean size of arctic circle landings is skewed heavily by meteorite "5262" which is a massive 58.2 tonnes (2nd largest in the entire cleaned data) 

# Landings by year

```{r}
# Earliest landing
meteorite_landings_cleaned %>% 
  slice_min(year)

# per century
source("century_function.R")
meteorite_landings_cleaned %>% 
  mutate(century = century(year))%>% 
  group_by(century) %>% 
  summarise(total_meteorites = length(id),
            mean_size = mean(mass_g))

# why is this not working?
# it is correctly selecting and grouping the centuries but returning 21th century
# works fine when tested in function script
```
* Most reported meteorite landings in 20th century
* largest mean size of meteorites in 17th century 



  


















